---
---

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

### a) Create an Excel spreadsheet with three columns; name, degree program, and years at UF

### b) Add your information to it

### c) Optional: Add some of your classmates information (recall from class introductions, or, re-introduce yourself after class)

### d) Read this file into R and assign it to an object called `data` (just like we did in class)

```{r}
#| label: 1d

```

```{=typst}
// Hint: You'll need a new package to read Excel files, between Google and asking your friends, you should be able to figure it out

// FYI: This is a special kind of code block (a raw typst comment) which is a great way of adding notes to your file that won't show up in the final pdf such as notes to yourself, feedback from reviewers, questions/prompts, etc.. It's also how I will give your assignment feedback. You don't need to worry about using them for now, but you might find them useful later on for planning your final projects etc.
```
## Question Two

### a) Pick any single data file from IPEDS that peaks your interest

### b) Download it and save it to your `data` folder

### c) Read it into R and assign it to an object called `data_ipeds`

```{r}
#| label: 2c

```

```{=typst}
// Once complete, turn in the .R script (no data etc.), .qmd file, and the PDF output to Canvas by the due date (Tuesday 12:00pm following the lesson).
// Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
```
