---
---

Use the `hsls_small.csv` data set from the lesson answer the following questions

- You will need to use variables on math scores, students' poverty level, postsecondary attendance, sex, family income, parental education

> Hint: You're going to need the [code book](https://nces.ed.gov/datalab/onlinecodebook) to identify the necessary variables

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

**a)** Conduct a t-test to compare math scores between students below 185% of the federal poverty line and those above it. Is there a statistically significant difference?

```{r}
#| label: 1a


```

**b)** Make a plot to visualize the difference.

```{r}
#| label: 1b


```

## Question Two

**a)** Fit a logistic regression predicting postsecondary attendance using math score, sex, family income, and parental education. 

> Hint: Logistic regression is what you want to use when your outcome variable is binary (0 or 1) instead of a continuous variable. You might want to Google to find out what function you need for fitting a logistic regression. 

```{r}
#| label: 2a


```

**b)** Create a nicely formatted output table using `stargazer` or `gtsummary` for the model from 2a. What are some significant predictors based on your model results?

```{r}
#| label: 2b


```


```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) and the rendered PDF to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
